---
title: "First Knit"
author: "Jose Guzman"
date: "Date,11/16/2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  

###my answer     
  
I sit in the middle of the classroom; sometimes in the front. I started in back but moved forward so I could pay more attention. On a scale of 1-10 I feel 5 about the re-assignment of seating. In my other classes, I tend to sit in the middle as well.    
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

###my answer     
  
My full name is Jose Trinidad Guzman. My friends refer to me as "Hoezay", it has stuck with me since highschool. I prefer to be called "Hoezay".   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  
My aspiration in life is to become a nurse practioner. I am currently finishing my general ED so I can transfer to a nursing program in Glendale. Currently, all my science classes are the most interesting to me.    
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  
I have travled to Mexicao a lot through out my childhood and my adolescent life. My grandfather lives in Mexico City but he is originally from Nayarit Mexico. I have never been in the military but If I was; I would choose the air force.    
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

###my answer     
  
I need a B or higher in the class to move on with the nursing program. My goal is to tackle down each assignment one by one. Meaning, I finish all the quizzes first, then move on to the homework and finally the projects.    
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  
On a scale from 1-10 my computer literacy is at a solid 7. I am not oblivous to computers but I am also not a pro. I have a computer at home, it is a Mac desktop pro. I have internet access at home that comes in handy. I drive to class everyday in my 2012 Honda civic. I attended Rosamond High School and graduated in 2016. I am employed with JWCH inc. It is a non profit clinic and my postion is referral specialist.    
  




